# Parallelization

For all parallel calculations, *CopyKit* adopts the [BiocParallel](https://www.bioconductor.org/packages/devel/bioc/vignettes/BiocParallel/inst/doc/Introduction_To_BiocParallel.pdf) framework. 

Make sure to read the BiocParallel vignette to choose the best parameters for your machine. An example workflow can be done as follows:

We use `BiocParallel::register()` function to register the number of workers desired.

```{r registering_fake, eval=FALSE}
library(BiocParallel)
register(MulticoreParam(progressbar = T), default = T)
```

```{r registering_true, echo=FALSE}
library(BiocParallel)
register(MulticoreParam(progressbar = F), default = T)
```

The default parameter can be confirmed with:
```{r default}
BiocParallel::bpparam()
```

Make sure to check the number of workers in use. The higher the number of workers
available the faster *CopyKit* computations will perform.

The argument *progressbar* allows for a helpful progression bar while the process is being run.

After this setup *CopyKit* parallelized functions will automatically recognize these parameters and run in parallel.

Running parallel process is highly recommended to speed up CopyKit calculations.



