# Parallelization

Whenever possible, *CopyKit* uses the [BiocParallel](https://www.bioconductor.org/packages/devel/bioc/vignettes/BiocParallel/inst/doc/Introduction_To_BiocParallel.pdf) framework. 

Running parallel process is highly recommended to speed up *CopyKit* calculations.

Make sure to read the BiocParallel [vignette](https://www.bioconductor.org/packages/devel/bioc/vignettes/BiocParallel/inst/doc/Introduction_To_BiocParallel.pdf) to choose the best parameters for your machine and OS. 

<!--- I suggest you use cores or workers/cores. I am not as familiar with the term workers. --->
Use `BiocParallel::register()` function to register the number of workers desired.

```{r registering_fake, eval=FALSE}
library(BiocParallel)
register(MulticoreParam(progressbar = T), default = T)
```

```{r registering_true, echo=FALSE}
library(BiocParallel)
register(MulticoreParam(progressbar = F), default = T)
```

Confirm parameters:
```{r default}
BiocParallel::bpparam()
```

Make sure to check the number of cores to be used. 
On Unix, Linux and Mac systems the number of workers will be the number of cores found using parallel::detectCores() minus 2. 
If this not defined it will set it 1. Therefore, it is strongly suggested that you check the number of cores to get the best parallel optimization.

To visually monitor the progress, you can use the argument *progressbar* to obtain a progress bar. 
