# Analysis and Visualization module

The analysis and visualization module from CopyKit work in synergy to help you analyze and assess the results from your day.

The analysis module provides the following functions: `runUmap()`, `calcInteger()`, `findSuggestedK()`, `findClusters()`, `calcConsensus()` and `runPhylo()`.

The visualization module functions are: `plotMetrics()`, `plotRatio()`, `plotUmap()`, `plotHeatmap()`, `plotConsensusLine()` and `plotGeneCopy()`.

## runUmap()

runUmap uses generates a [UMAP](https://umap-learn.readthedocs.io/en/latest/) reduced dimensions embedding, the resulting embedding is stored within the scCNA reducedDim slot and is an important pre-processing step to the findClusters feature.

```{r run_umap}
tumor <- runUmap(tumor)
```

Additional arguments to control umap parameters can be passed on to`runUmap()` with the '...' argument.

```{r}
tumor <- runUmap(tumor, n_neighbors = 30, min_dist = 0)
```

## plotUmap()

`plotUmap()` can be used to plot the reduced dimensional embedding. plotUmap can be colored by any element of the metadata with the argument 'label', this will be shown in a later section.

```{r}
plotUmap(tumor)
```

## Clustering

The `findClusters()` function will use the reduced dimensional embedding resulting from runUmap to perform clustering of superclones and subclones.

When clustering for superclones `findClusters()` creates a graph representation of the dataset reduced dimension embedding using a shared nearest neighbor algorithm (SNN), from this graph the connected components are extracted and generally represent high-level structures that share large, lineage defining copy number events.

CopyKit can also be used to detect subclones, i. e. groups of cells containing a unique copy number event per cluster, to do so the umap embedding is again used as the pre-processing step, this time to perform a density-based clustering with [hdbscan](https://hdbscan.readthedocs.io/en/latest/how_hdbscan_works.html) as seen in the work from Laks *et al.* [@RN6].

### findSugestedK()

Density-based clustering requires input of the k neighbors, frequently chosen ad hoc. To help with parametrization, CopyKit provides the helper findSuggestedK function. findSuggestedK performs a clustering bootstrapping over a range of k values and returns the value that maximizes the jaccard similarity. While findSuggestedK does not guarantee that the suggested value will result in optimal clustering but provides a guide that maximizes cluster stability.

```{r find_suggested_k}
tumor <- findSuggestedK(tumor)
```

The suggested value is stored into the metadata and can be access at:
```{r find_sug_meta}
S4Vectors::metadata(tumor)$suggestedK
```

### findClusters()

To run `findClusters()` simply use the function in the CopyKit object and provide the k value with the arguments 'k_superclones' and 'k_subclones'.
*NOTE:* k_superclones and k_subclones can be used concurrently. Only k_subclones is a mandatory field.


```{r findCl_withparam}
tumor <- findClusters(tumor,
                      k_superclones = 30,
                      k_subclones = 15)
```

If `findSuggestedK()` was used and the argument 'k_subclones' is not provided, `findClusters()` will automatically use the value resulting from `findSuggestedK()` that was stored into the metadata:

```{r findCL_findSuggested}
tumor <- findClusters(tumor)
```




